Statistical Guarantees for Local Spectral Clustering on Random Neighborhood Graphs

### 2021-09-05 jmlr/revision2/appendix.tex
Through checking + copy-editting Appendices A and B.

\noindent The proofs of our major theorems largely consist of (at most) three modular parts.
\begin{enumerate}
	\item \textbf{Fixed graph results.} Results which hold with respect to an arbitrary graph $G$, and are stated with respect to functionals (i.e. normalized cut, conductance, and local spread) of $G$;
	\item \textbf{Sample-to-population results.} For the specific choice $G = G_{n,r}$, w  e relate the aforementioned functionals to their population analogues. 
	\item \textbf{Bounds on population functionals.} (In the case of density clustering only.) When the candidate cluster is a $\lambda$-density cluster, we bound the population functionals by a function of $\lambda$, as well as the other relevant parameters introduced in Section~\ref{sec:ppr_density_cluster}.
\end{enumerate}

@@

\section{Fixed graph results}
\label{apdx:fixed_graph}
In this appendix, we give all results that hold with respect to an arbitrary graph $G$. For the convenience of the reader, we begin by reviewing some notation from the main text, and also introduce some new notation.

\paragraph{Notation.}
The graph $G = (V,E)$ is an undirected and connected but otherwise arbitrary graph, defined over vertices $V = \{1,\ldots,n\}$ with $m = |E|$ total edges. The adjacency matrix of $G$ is $A$, the degree matrix is $D$, and the lazy random walk matrix over $G$ is $W = (I + D^{-1}A)/2$. If the lazy random walk originates at a node $v$, the distribution of the lazy random walk $q_v^{(t)} := q(v,t;G)$ after $t$ steps is $q_v^{(t)} := e_v W^t$, with stationary distribution $\pi := \pi(G) := \lim_{t \to \infty} q_v^{(t)}$ with entries $\pi(u) = \deg(u;G)/\vol(u;G)$.

For a starting distribution $s$ (by distribution we mean a vector with non-negative entries), the PPR vector $p_s = p(s,\alpha;G)$ is the solution of
\begin{equation}
\label{eqn:ppr}
p_s = \alpha s + (1 - \alpha) p_s W.
\end{equation}
When $s = e_v$, we write $p_v := p_{e_v}$. It is easy to check that $p_s = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t q_s^{(t)}$.  Note that $s$ need not be a probability distribution (i.e. its entries need not sum to $1$) to make sense of~\eqref{eqn:ppr}.

@@

The conductance of $V$ is abbreviated as $\Psi(G) := \Psi(V;G)$, and likewise for the local spread $s(G) := s(V;G)$. Finally, for convenience we introduce the following functionals:
\begin{equation*}
\begin{aligned}
& d_{\max}(C; G) := \max_{u \in C} \deg(u; G), && d_{\min}(C; G) := \min_{u \in C} \deg(u;G) \\
& d_{\max}(G) := d_{\max}(V;G),~~ && d_{\min}(G) := d_{\min}(V; G)
\end{aligned}
\end{equation*}
We note that $d_{\min}(G)^2 \leq d_{\min}(G) \cdot n \leq \vol(G) \leq n \cdot d_{\max}(G)$, and that for any $S \subseteq V$, $|S| \cdot d_{\min}(G) \leq \vol(S;G)$ (where $|S|$ is the cardinality of $S$.)

@@

\paragraph{Proof of Lemma~\ref{lem:zhu}.}
As mentioned in the main text, Lemma~\ref{lem:zhu} is equivalent, up to constants, to Lemma~3.4 in \cite{zhu2013}, and the proof of Lemma~\ref{lem:zhu} proceeds along very similar lines to the proof of that lemma. In fact, we directly use the following three inequalities, derived in that work:
\begin{itemize}
	\item \textbf{(c.f. Lemma 3.2 of \cite{zhu2013})} For any seed node $v \in C$, the PPR vector is lower bounded,
	\begin{equation}
	\label{pf:zhu1}
	\wt{p}_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u),~~\textrm{for every $u \in C$.}
	\end{equation}
	\item \textbf{(c.f. Corollary 3.3 of \cite{zhu2013})} For any seed node $v \in C$, there exists a so-called leakage distribution $\ell = \ell(v)$ such that $\mathrm{supp}(\ell) \subseteq C$, $\|\ell\|_1 \leq 2\Phi(C;G)/\alpha$, and 
	\begin{equation}
	\label{pf:zhu2}
	p_v(u) \geq \wt{p}_v(u) - \wt{p}_{\ell}(u),~~\textrm{for every $u \in C$.}
	\end{equation}
	\item \textbf{(c.f. Lemma 3.1 of \cite{zhu2013})} There exists a set $C^g \subset C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C;G)$ such that for any seed node $v \in C^g$, the following inequality holds
	\begin{equation}
	\label{pf:zhu3}
	p_v(C^c) \leq 2\frac{\Phi(C;G)}{\alpha}.
	\end{equation}
\end{itemize}
teWe use~\eqref{pf:zhu1}-\eqref{pf:zhu3} to separately upper bound $\vol(S_{\beta,v} \setminus C;G)$, $\vol(C^{\mathrm{int}} \setminus S_{\beta,v};G)$ and $\vol(C^{\mathrm{bdry}} \setminus S_{\beta,v};G)$; here $C^{\mathrm{int}} \cup C^{\mathrm{bdry}} = C$ is a partition of $C$, with
\begin{equation*}
C^{\mathrm{int}} := \Bigl\{u \in C: \deg(u;\wt{G}) > \bigl(1 - \alpha \cdot \beta \cdot \vol(C;G)\bigr) \deg(u;G) \Bigr\},
\end{equation*}
consisting of those vertices $u \in C$ with sufficient large degree in $\wt{G}$.

First we upper bound $\vol(S_{\beta,v} \setminus C;G)$. Observe that for any $u \in S_{\beta,v} \setminus C$, $p_v(u) > \beta \cdot \deg(u;G)$. Summing up over all such vertices, from~\eqref{pf:zhu3} we conclude that
\begin{equation}
\label{pf:zhu3.5}
\vol(S_{\beta,v} \setminus C; G) \leq \frac{p_v(C^c)}{\beta} \leq 2\frac{\Phi(C;G)}{\beta \cdot \alpha}.
\end{equation}

Next we upper bound $\vol(C^{\mathrm{int}} \setminus S_{\beta,v};G)$. From~\eqref{pf:zhu1} and~\eqref{pf:zhu2} we see that 
\begin{equation*}
p_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u) - \wt{p}_{\ell}(u)~~\textrm{for all $u \in C$.}
\end{equation*}
If additionally $u \not\in S_{\beta,v}$ then $p_v(u) \leq \beta \deg(u;G)$, and for all such $u \in C \setminus S_{\beta,v}$,
\begin{equation}
\label{pf:zhu4}
\frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u) -  \beta\deg(u;G) \leq \wt{p}_{\ell}(u).
\end{equation}
On the other hand, for any $u \in C^{\mathrm{int}}$ it holds that
\begin{equation*}
\wt{\pi}(u) = \frac{\deg(u;\wt{G})}{\vol(\wt{G})} \geq \frac{\deg(u;\wt{G})}{\vol(G)} \geq \frac{(1 - \alpha \beta \vol(C;G))\deg(u;G)}{\vol(C;G)};
\end{equation*}
by plugging this in to~\eqref{pf:zhu4} we obtain
\begin{equation*}
\biggl(\frac{3(1 - \alpha \beta \vol(C;G))\cdot\bigl(1 - \alpha \tau_{\infty}(\wt{G})\bigr)}{4\vol(C;G)} - \beta\biggr) \cdot \deg(u;G) \leq \wt{p}_{\ell}(u),~~\textrm{for all $u \in C^{\mathrm{int}} \setminus S_{\beta,v}$};
\end{equation*}
and summing over all such $u$ gives
\begin{equation*}
\biggl(\frac{3(1 - \alpha \beta \vol(C;G))\cdot\bigl(1 - \alpha \tau_{\infty}(\wt{G})\bigr)}{4\vol(C;G)} - \beta\biggr) \cdot \vol\bigl(C^{\mathrm{int}} \setminus S_{\beta,v}; G\bigr) \leq \wt{p}_{\ell}\bigl(C^{\mathrm{int}} \setminus S_{\beta,v}\bigr) \leq 2\frac{\Phi(C;G)}{\alpha}.
\end{equation*}
The upper bounds on $\alpha$ and $\beta$ in~\eqref{eqn:zhu_condition} imply
\begin{equation*}
\biggl(\frac{3(1 - \alpha \beta \vol(C;G))\cdot\bigl(1 - \alpha \tau_{\infty}(\wt{G})\bigr)}{4\vol(C;G)} - \beta\biggr) \geq \frac{2}{3}\beta,
\end{equation*}
and we conclude that
\begin{equation}
\label{pf:zhu5}
\vol(C^{\mathrm{int}} \setminus S_{\beta,v}; G) \leq \frac{3\Phi(C;G)}{\alpha\beta}.
\end{equation}

Finally, we upper bound $\vol(C^{\mathrm{bdry}} \setminus S_{\beta,v};G)$. Indeed, for any $u \in C^{\mathrm{bdry}}$,
\begin{equation*}
\frac{1}{\vol(C;G)}\sum_{w \not\in C} \1((u,w) \in E) \geq \alpha \cdot \beta \cdot \deg(u;G)
\end{equation*}
and summing over all such vertices yields
\begin{equation}
\label{pf:zhu6}
\vol(C^{\mathrm{bdry}};G) \leq \frac{1}{\alpha \beta \vol(C;G)}\sum_{\substack{u \in C^{\mathrm{bdry}} \\ w \not\in C}} \1((u,w) \in E) \leq \frac{\Phi(C;G)}{\alpha \cdot \beta}.
\end{equation} 
The claim follows upon summing the upper bounds in~\eqref{pf:zhu3.5}, \eqref{pf:zhu5} and~\eqref{pf:zhu6}.

@@

These quantities admit a natural interpretation in terms of random walks. For $u \in C$, $\ell^{(t)}(u)$ is the probability that a lazy random walk over $G$ originating at $v$ stays within $\wt{G}$ for $t$ steps, arriving at $u$ on the $t$th step, and then ``leaks out'' of $C$ on the $(t + 1)$st step. On the other hand, for $u \not\in C$, $s^{(t)}(u)$ is the probability that a lazy random walk over $G$ originating at $v$ stays within $\wt{G}$ for $t$ steps and is then ``soaked up'' into $u$ on the $(t + 1)$st step. The vectors $\ell$ and $s$ then give the total mass leaked and soaked, respectively, by the PPR vector.

@@

\paragraph{Proof of Lemma~\ref{lem:ppr_uniform_bound}.}
	We first show~\eqref{eqn:ppr_uniform_bound_C}. From~\eqref{pf:zhu3} and~\eqref{pf:zhu2}, we have that
	\begin{equation*}
	p_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u) - \wt{p}_{\ell}(u)~~\textrm{for all $u \in C$,}
	\end{equation*}
	where $\ell$ has support $\mathrm{supp}(\ell) \subseteq C$ with $\|\ell\|_1 \leq 2\Phi(C;G)/\alpha$. Recalling that $u \in C_{o}$ implies that $u \not\in \mathrm{supp}(C_{o})$, as a consequence of~\eqref{pf:interpolator_bound_max_entry}, 
	\begin{equation*}
	\wt{p}_{\ell}(u) \leq \frac{\|\ell\|_1}{d_{\min}(\wt{G})}~~\textrm{for all $u \in C_{o}$,}
	\end{equation*}
	establishing~\eqref{eqn:ppr_uniform_bound_C}. The proof of~\eqref{eqn:ppr_uniform_bound_Cprime} follows similarly:
	\begin{equation*}
	p_v(u) = p_s(u) \overset{(i)}{\leq} \frac{\|s\|_1}{d_{\min}(C';G)} = \frac{\|\ell\|_1}{d_{\min}(C';G)},~~\textrm{for all $u \in C_{o}'$},
	\end{equation*}
	where the presence of $d_{\min}(C';G)$ on the right hand side of $(i)$ can be verified by inspecting~\eqref{pf:interpolator_bound_max_entry_inductive_step}.

@@

	Now, we claim that for each $k_j$, it holds that
	\begin{equation}
	\label{pf:mixing_random_walk_inductive_step}
	q_v^{(t)}[k_j] \leq \frac{1}{2}\Bigl(q_v^{(t - 1)}[k_j - \wb{k}_j \Psi(G)] + q_v^{(t - 1)}[k_j + \wb{k}_j \Psi(G)]\Bigr).
	\end{equation}
	To establish this claim, we note that for any $u \in V$
	\begin{equation*}
	q_v^{(t)}(u) = \frac{1}{2}q_v^{(t - 1)}(u) + \frac{1}{2}\sum_{w \in V}q_v^{(t - 1)}(w,u) = \frac{1}{2} \sum_{w \in V} \bigl(q_v^{(t - 1)}(u,w) + q_v^{(t - 1)}(w,u)\bigr),
	\end{equation*}
	and consequentially for any $S \subset V$,
	\begin{align*}
	q_v^{(t)}(S) & = \frac{1}{2}\bigl\{q_v^{(t - 1)}(\mathrm{in}(S)) +  q_v^{(t - 1)}(\mathrm{out}(S))\bigr\} \\
	& = \frac{1}{2}\bigl\{q_v^{(t - 1)}\bigl(\mathrm{in}(S) \cup \mathrm{out}(S)\bigr) +  q_v^{(t - 1)}\bigl(\mathrm{in}(S) \cap \mathrm{out}(S)\bigr)\bigr\}
	\end{align*}
	where $\mathrm{in}(S) = \{(u,w) \in E: u \in S\}$ and $\mathrm{out}(S) = \{(w,u) \in E: w \in S\}$. We deduce that
	\begin{align*}
	q_v^{(t)}[k_j] = q_v^{(t)}(S_j) & = \frac{1}{2}\bigl\{q_v^{(t - 1)}\bigl(\mathrm{in}(S_j) \cup \mathrm{out}(S_j)\bigr) +  q_v^{(t - 1)}\bigl(\mathrm{in}(S_j) \cap \mathrm{out}(S_j)\bigr)\bigr\} \\
	& \leq \frac{1}{2}\bigl\{q_v^{(t - 1)}\bigl[|\mathrm{in}(S_j) \cup \mathrm{out}(S_j)|\bigr] +  q_v^{(t - 1)}\bigl[|\mathrm{in}(S_j) \cap \mathrm{out}(S_j)|\bigr]\bigr\} \\
	& = \frac{1}{2}\bigl\{q_v^{(t - 1)}\bigl[k_j + \mathrm{cut}(S_j;G)\bigr] +  q_v^{(t - 1)}\bigl[k_j - \mathrm{cut}(S_j;G)\bigr]\bigr\} \\
	& \leq \frac{1}{2}\bigl\{q_v^{(t - 1)}\bigl[k_j + \wb{k}_j\Phi(S_j;G)\bigr] +  q_v^{(t - 1)}\bigl[k_j - \wb{k}_j\Phi(S_j;G)\bigr]\bigr\} \\
	& \leq \frac{1}{2}\bigl\{q_v^{(t - 1)}\bigl[k_j + \wb{k}_j\Psi(G)\bigr] +  q_v^{(t - 1)}\bigl[k_j - \wb{k}_j\Psi(G)\bigr]\bigr\},
	\end{align*}
	establishing~\eqref{pf:mixing_random_walk_inductive_step}. The final two inequalities both follow from the concavity of $q_v^{(t)}[\cdot]$.

@@

\subsection{Proof of Proposition~\ref{prop:pointwise_mixing_time}}
\label{subsec:pf_prop_pointwise_mixing_time}
To prove Proposition~\ref{prop:pointwise_mixing_time}, we will upgrade from an upper bound on the total variation distance between $q_v^{(t)}$ and $\pi$ to the desired uniform upper bound. The \emph{total variation distance} between distributions $q$ and $p$ is
\begin{equation*}
\mathrm{TV}(q,p) := \frac{1}{2}\sum_{u \in v} \bigl|q(u) - p(u)\bigr|
\end{equation*}
It follows from the representation~\eqref{eqn:lovasz_simonovits} that
\begin{equation*}
\mathrm{TV}(q,\pi) = \max_{S \subseteq V} \Bigl\{q(S) - \pi(S)\Bigr\} = \max_{j = 1,\ldots,n} \Bigl\{q(S_j) - \pi(S_j)\Bigr\} = \max_{k \in [0,2m]} h_q(k),
\end{equation*}
so that Theorem~\ref{thm:mixing_time_rw} gives an upper bound on $\mathrm{TV}(q_v^{(t)},\pi)$. We can then use the following result to upgrade to a uniform upper bound.

\begin{lemma}
	\label{lem:tv_to_pointwise}
	For any $t \in \mathbb{N}$,
	\begin{equation*}
	\max_{u \in V} \Bigl\{\frac{\pi(u) - q_v^{(t + 1)}(u)}{\pi(u)}\Bigr\} \leq \frac{2 \cdot \mathrm{TV}(q_v^{(t)}, \pi)}{s(G)}.
	\end{equation*}
\end{lemma}

>>>>

\noindent The proofs of our major theorems largely consist of (at most) three modular parts.
\begin{enumerate}
	\item \textbf{Fixed graph results.} Results which hold with respect to an arbitrary graph $G$, and are stated with respect to functionals (i.e. normalized cut, conductance, and local spread) of $G$;
	\item \textbf{Sample-to-population results.} For the specific choice $G = G_{n,r}$, results relating the aforementioned functionals to their population analogues. 
	\item \textbf{Bounds on population functionals.} (In the case of density clustering only.) When the candidate cluster is a $\lambda$-density cluster, bounds on population functionals as a function of $\lambda$, as well as the other relevant parameters introduced in Section~\ref{sec:ppr_density_cluster}.
\end{enumerate}

@@

\section{Fixed graph results}
\label{apdx:fixed_graph}
In this section, we give all results that hold with respect to an arbitrary graph $G$. For the convenience of the reader, we begin by reviewing some notation from the main text, and also introduce some new notation.

\paragraph{Notation.}
The graph $G = (V,E)$ is an undirected and connected but otherwise arbitrary graph, defined over vertices $V = \{1,\ldots,n\}$ with $m = |E|$ total edges. The adjacency matrix of $G$ is $A$, the degree matrix is $D$, and the lazy random walk matrix over $G$ is $W = (I + D^{-1}A)/2$. The lazy random walk originating at node $v \in V$ has distribution $q(v,t;G) = e_vW^t$ after $t$ steps; we use the notational shorthand $q_v^{(t)} := q(v,t;G)$. The stationary distribution of the lazy random walk is $\pi := \pi(G) := \lim_{t \to \infty} q_v^{(t)}$ is given by $\pi(u) = \deg(u;G)/\vol(u;G)$.

For a starting distribution $s$ (by distribution we mean a vector with non-negative entries), the PPR vector $p_s = p(s,\alpha;G)$ is the solution to
\begin{equation}
\label{eqn:ppr}
p_s = \alpha s + (1 - \alpha) p_s W.
\end{equation}
When $s = e_v$, we write $p_v := p_{e_v}$. It is easy to check that $p_s = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t q_s^{(t)}$.  Note that $s$ need not be a probability distribution (i.e. its entries need not sum to $1$) to make sense of~\eqref{eqn:ppr}.

@@

The conductance of $V$ is abbreviated as $\Psi(G) := \Psi(V;G)$, and likewise for the local spread $s(G) := s(V;G)$. Finally, for convenience we introduce the following functionals:
\begin{equation*}
\begin{aligned}
& d_{\max}(C; G) := \max_{u \in C} \deg(u; G), && d_{\min}(C; G) := \min_{u \in C} \deg(u;G) \\
& d_{\max}(G) := d_{\max}(V;G),~~ && d_{\min}(G) := d_{\min}(V; G)
\end{aligned}
\end{equation*}
We note that $d_{\min}(G)^2 \leq d_{\min}(G) \cdot n \leq \vol(G) \leq d_{\max}(G) \cdot n$, and that for any $S \subseteq V$, $|S| \cdot d_{\min}(G) \leq \vol(S;G)$ (where $|S|$ is the cardinality of $S$.)

@@

\paragraph{Proof of Lemma~\ref{lem:zhu}.}
As mentioned in the main text, Lemma~\ref{lem:zhu} is equivalent, up to constants, to Lemma~3.4 in \cite{zhu2013}, and the proof of Lemma~\ref{lem:zhu} proceeds along very similar lines to the proof of that lemma. In fact, we directly use the following three inequalities, derived in that work:
\begin{itemize}
	\item \textbf{(c.f. Lemma 3.2 of \cite{zhu2013})} For any seed node $v \in C$, the PPR vector is lower bounded,
	\begin{equation}
	\label{pf:zhu1}
	\wt{p}_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u),~~\textrm{for every $u \in C$.}
	\end{equation}
	\item \textbf{(c.f. Corollary 3.3 of \cite{zhu2013})} For any seed node $v \in C$, there exists a so-called leakage distribution $\ell = \ell(v)$ such that $\mathrm{supp}(\ell) \subseteq C$, $\|\ell\|_1 \leq 2\Phi(C;G)/\alpha$, and 
	\begin{equation}
	\label{pf:zhu2}
	p_v(u) \geq \wt{p}_v(u) - \wt{p}_{\ell}(u),~~\textrm{for every $u \in C$.}
	\end{equation}
	\item \textbf{(c.f. Lemma 3.1 of \cite{zhu2013})} There exists a set $C^g \subset C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C;G)$ such that for any seed node $v \in C^g$, the following inequality holds
	\begin{equation}
	\label{pf:zhu3}
	p_v(C^c) \leq 2\frac{\Phi(C;G)}{\alpha}.
	\end{equation}
\end{itemize}
We use~\eqref{pf:zhu1}-\eqref{pf:zhu3} to separately upper bound $\vol(S_{\beta,v} \setminus C;G)$, $\vol(C^{\mathrm{int}} \setminus S_{\beta,v};G)$ and $\vol(C^{\mathrm{bdry}} \setminus S_{\beta,v};G)$; here $C^{\mathrm{int}} \cup C^{\mathrm{bdry}} = C$ is a partition of $C$, with
\begin{equation*}
C^{\mathrm{int}} := \Bigl\{u \in C: \deg(u;\wt{G}) > \bigl(1 - \alpha \cdot \beta \cdot \vol(C;G)\bigr) \deg(u;G) \Bigr\},
\end{equation*}
consisting of those vertices $u \in C$ with sufficient large degree in $\wt{G}$.

First we upper bound $\vol(S_{\beta,v} \setminus C;G)$. Observe that for any $u \in S_{\beta,v} \setminus C$, $p_v(u) > \beta \cdot \deg(u;G)$. Summing up over all such vertices, from~\eqref{pf:zhu3} we conclude that
\begin{equation}
\label{pf:zhu3.5}
\vol(S_{\beta,v} \setminus C; G) \leq \frac{p_v(C^c)}{\beta} \leq 2\frac{\Phi(C;G)}{\beta \cdot \alpha}.
\end{equation} 
Next we upper bound $\vol(C^{\mathrm{int}} \setminus S_{\beta,v};G)$. From~\eqref{pf:zhu1} and~\eqref{pf:zhu2} we see that 
\begin{equation*}
p_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u) - \wt{p}_{\ell}(u)~~\textrm{for all $u \in C$.}
\end{equation*}
If additionally $u \not\in S_{\beta,v}$ then $p_v(u) \leq \beta \deg(u;G)$, and for all such $u \in C \setminus S_{\beta,v}$,
\begin{equation}
\label{pf:zhu4}
\frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u) -  \beta\deg(u;G) \leq \wt{p}_{\ell}(u).
\end{equation}
On the other hand, for any $u \in C^{\mathrm{int}}$ it holds that
\begin{equation*}
\wt{\pi}(u) = \frac{\deg(u;\wt{G})}{\vol(\wt{G})} \geq \frac{\deg(u;\wt{G})}{\vol(G)} \geq \frac{(1 - \alpha \beta \vol(C;G))\deg(u;G)}{\vol(C;G)};
\end{equation*}
by plugging this in to~\eqref{pf:zhu4} we obtain
\begin{equation*}
\biggl(\frac{3(1 - \alpha \beta \vol(C;G))\cdot\bigl(1 - \alpha \tau_{\infty}(\wt{G})\bigr)}{4\vol(C;G)} - \beta\biggr) \cdot \deg(u;G) \leq \wt{p}_{\ell}(u),~~\textrm{for all $u \in C^{\mathrm{int}} \setminus S_{\beta,v}$};
\end{equation*}
and summing over all such $u$ gives
\begin{equation*}
\biggl(\frac{3(1 - \alpha \beta \vol(C;G))\cdot\bigl(1 - \alpha \tau_{\infty}(\wt{G})\bigr)}{4\vol(C;G)} - \beta\biggr) \cdot \vol\bigl(C^{\mathrm{int}} \setminus S_{\beta,v}; G\bigr) \leq \wt{p}_{\ell}\bigl(C^{\mathrm{int}} \setminus S_{\beta,v}\bigr) \leq 2\frac{\Phi(C;G)}{\alpha}.
\end{equation*}
The upper bounds on $\alpha$ and $\beta$ in~\eqref{eqn:zhu_condition} imply
\begin{equation*}
\biggl(\frac{3(1 - \alpha \beta \vol(C;G))\cdot\bigl(1 - \alpha \tau_{\infty}(\wt{G})\bigr)}{4\vol(C;G)} - \beta\biggr) \geq \frac{2}{3}\beta,
\end{equation*}
and we conclude that
\begin{equation}
\label{pf:zhu5}
\vol(C^{\mathrm{int}} \setminus S_{\beta,v}; G) \leq \frac{3\Phi(C;G)}{\alpha\beta}.
\end{equation}
Finally, we upper bound $\vol(C^{\mathrm{bdry}} \setminus S_{\beta,v};G)$. Indeed, for any $u \in C^{\mathrm{bdry}}$,
\begin{equation*}
\frac{1}{\vol(C;G)}\sum_{w \not\in C} \1((u,w) \in E) \geq \alpha \cdot \beta \cdot \deg(u;G)
\end{equation*}
and summing over all such vertices yields
\begin{equation}
\label{pf:zhu6}
\vol(C^{\mathrm{bdry}};G) \leq \frac{1}{\alpha \beta \vol(C;G)}\sum_{\substack{u \in C^{\mathrm{bdry}} \\ w \not\in C}} \1((u,w) \in E) \leq \frac{\Phi(C;G)}{\alpha \cdot \beta}.
\end{equation} 
The claim follows upon summing the upper bounds in~\eqref{pf:zhu3.5}, \eqref{pf:zhu5} and~\eqref{pf:zhu6}.

@@

These quantities admit a natural interpretation in terms of random walks. For $u \in C$, $\ell^{(t)}(u)$ is the probability that a lazy random walk over $G$ originating at $v$ stays within $C$ for $t$ steps, arriving at $u$ on the $t$th step, and then ``leaks out'' of $C$ on the $(t + 1)$st step. On the other hand, for $u \not\in C$, $s^{(t)}(u)$ is the probability that a lazy random walk over $G$ originating at $v$ stays within $C$ for $t$ steps and is then ``soaked up'' into $u$ on the $(t + 1)$st step. The vectors $\ell$ and $s$ then give the total mass leaked and soaked, respectively, by the PPR vector.

@@

\paragraph{Proof of Lemma~\ref{lem:ppr_uniform_bound}.}
	We first show~\eqref{eqn:ppr_uniform_bound_C}. From~\eqref{pf:zhu3} and~\eqref{pf:zhu2}, we have that
	\begin{equation*}
	p_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u) - \wt{p}_{\ell}(u)~~\textrm{for all $u \in C$,}
	\end{equation*}
	where $\ell$ has support $\mathrm{supp}(\ell) \subseteq C$ with $\|\ell\|_1 \leq 2\Phi(C;G)/\alpha$. Recalling that $u \in C_{o}$ implies that $u \not\in \mathrm{supp}(\ell)$, as a consequence of~\eqref{pf:interpolator_bound_max_entry}, 
	\begin{equation*}
	\wt{p}_{\ell}(u) \leq \frac{\|\ell\|_1}{d_{\min}(\wt{G})}~~\textrm{for all $u \in C_{o}$,}
	\end{equation*}
	establishing~\eqref{eqn:ppr_uniform_bound_C}. The proof of~\eqref{eqn:ppr_uniform_bound_Cprime} follows similarly:
	\begin{equation*}
	p_v(u) = p_s(u) \overset{(i)}{\leq} \frac{\|s\|_1}{d_{\min}(C';G)} = \frac{\|\ell\|_1}{d_{\min}(C';G)},~~\textrm{for all $u \in C_{o}'$},
	\end{equation*}
	where the presence of $d_{\min}(C';G)$ on the right hand side of $(i)$ can be verified by inspecting~\eqref{pf:interpolator_bound_max_entry_inductive_step}.

@@

	Now, we claim that for each $k_j$, it holds that
	\begin{equation}
	\label{pf:mixing_random_walk_inductive_step}
	q_v^{(t)}[k_j] \leq \frac{1}{2}\Bigl(q_v^{(t - 1)}[k_j - \wb{k}_j \Psi(G)] + q_v^{(t - 1)}[k_j + \wb{k}_j \Psi(G)]\Bigr).
	\end{equation}
	To establish this claim, we note that for any $u \in V$
	\begin{equation*}
	q_v^{(t)}(u) = \frac{1}{2}q_v^{(t - 1)}(u) + \frac{1}{2}\sum_{w \in V}q_v^{(t - 1)}(w,u) = \frac{1}{2} \sum_{w \in V} \bigl(q_v^{(t - 1)}(u,w) + q_v^{(t - 1)}(w,u)\bigr),
	\end{equation*}
	and consequently for any $S \subset V$,
	\begin{align*}
	q_v^{(t)}(S) & = \frac{1}{2}\bigl\{q_v^{(t - 1)}(\mathrm{in}(S)) +  q_v^{(t - 1)}(\mathrm{out}(S))\bigr\} \\
	& = \frac{1}{2}\bigl\{q_v^{(t - 1)}\bigl(\mathrm{in}(S) \cup \mathrm{out}(S)\bigr) +  q_v^{(t - 1)}\bigl(\mathrm{in}(S) \cap \mathrm{out}(S)\bigr)\bigr\}
	\end{align*}
	where $\mathrm{in}(S) = \{(u,w) \in E: u \in S\}$ and $\mathrm{out}(S) = \{(w,u) \in E: w \in S\}$. We deduce that
	\begin{align*}
	q_v^{(t)}[k_j] = q_v^{(t)}(S_j) & = \frac{1}{2}\bigl\{q_v^{(t - 1)}\bigl(\mathrm{in}(S_j) \cup \mathrm{out}(S_j)\bigr) +  q_v^{(t - 1)}\bigl(\mathrm{in}(S_j) \cap \mathrm{out}(S_j)\bigr)\bigr\} \\
	& \leq \frac{1}{2}\bigl\{q_v^{(t - 1)}\bigl[|\mathrm{in}(S_j) \cup \mathrm{out}(S_j)|\bigr] +  q_v^{(t - 1)}\bigl[|\mathrm{in}(S_j) \cap \mathrm{out}(S_j)|\bigr]\bigr\} \\
	& = \frac{1}{2}\bigl\{q_v^{(t - 1)}\bigl[k_j + \mathrm{cut}(S_j;G)\bigr] +  q_v^{(t - 1)}\bigl[k_j - \mathrm{cut}(S_j;G)\bigr]\bigr\} \\
	& \leq \frac{1}{2}\bigl\{q_v^{(t - 1)}\bigl[k_j + \wb{k}_j\Phi(S_j;G)\bigr] +  q_v^{(t - 1)}\bigl[k_j - \wb{k}_j\Phi(S_j;G)\bigr]\bigr\} \\
	& \leq \frac{1}{2}\bigl\{q_v^{(t - 1)}\bigl[k_j + \wb{k}_j\Psi(G)\bigr] +  q_v^{(t - 1)}\bigl[k_j - \wb{k}_j\Psi(G)\bigr]\bigr\},
	\end{align*}
	establishing~\eqref{pf:mixing_random_walk_inductive_step}. The final two inequalities both follow from the concavity of $q_v^{(t)}[\cdot]$.

@@

\subsection{Proof of Proposition~\ref{prop:pointwise_mixing_time}}
\label{subsec:pf_prop_pointwise_mixing_time}
To prove Proposition~\ref{prop:pointwise_mixing_time}, we first give an upper bound on the total variation distance between $q_v^{(t)}$ and its limiting distribution $\pi$, then upgrade to the desired uniform upper bound~\eqref{eqn:pointwise_mixing_time}. The \emph{total variation distance} between distributions $q$ and $p$ is
\begin{equation*}
\mathrm{TV}(q,p) := \frac{1}{2}\sum_{u \in v} \bigl|q(u) - p(u)\bigr|
\end{equation*}
It follows from the representation~\eqref{eqn:lovasz_simonovits} that
\begin{equation*}
\mathrm{TV}(q,\pi) = \max_{S \subseteq V} \Bigl\{q(S) - \pi(S)\Bigr\} = \max_{j = 1,\ldots,n} \Bigl\{q(S_j) - \pi(S_j)\Bigr\} = \max_{k \in [0,2m]} h_q(k),
\end{equation*}
so that Theorem~\ref{thm:mixing_time_rw} gives an upper bound on $\mathrm{TV}(q_v^{(t)},\pi)$. We can then use the following result to upgrade to a uniform upper bound.
